\chapter{Introduction}

\section{Dart}
Dart is the programming language used to code Flutter apps. Dart is another product by Google and released version 2.1, before Flutter, in November. It is designed for client development, such as for the web and mobile apps. It can also be used to build server and desktop applications.
\\ Dart is a client-optimized language for developing fast apps on any platform. Its goal is to offer the most productive programming language for multi-platform development, paired with a flexible execution runtime platform for app frameworks.
\\ Dart offers sound null safety, meaning that values can't be null unless you say they can be. With sound null safety, Dart can protect you from null exceptions at runtime through static code analysis. Unlike many other null-safe languages, when Dart determines that a variable is non-nullable, that variable is always non-nullable. Dart has a rich set of core libraries, providing essentials for many everyday programming tasks.
\\Dart programming language is a completely object-oriented language, including basic types such as int variables are also objects.
\section{Flutter}
 Google had its first ever release of Flutter 1.0 last December, after having it in beta mode for over 18 months. Flutter is Google's portable UI toolkit for
 crafting beautiful, natively compiled applications for mobile, 
 web, and desktop from a single codebase. Flutter works 
 with existing code, is used by developers and organizations
 around the world, and is free and open source. FLutter primarily uses Dart (a language also developed by google).        
 




