% \cleardoublepage
% \phantomsection
% \addcontentsline{toc}{chapter}{Abstract}
%\chapter*{\center Abstract}
{\Huge \centering \textbf{Abstract}\\}
% \vspace{0.09in}
\vspace{0.5in}
Nowadays Food Delivery App is the main important app most of the people are using as it gives them the chance to just order desired food and get it at home without going anywhere. Food app Development plays an important role in modern life because UI of app helps to interact with Hotels to order the food at home. So, latestly, Dart is the popular and very easy programming language used to code Flutter apps. Dart is another product by Google and released version 2.1, before Flutter, in November and Flutter is a free and open-source mobile UI framework created by Google and released in May 2017. Flutter allows us to create native mobile applications with only one code. It means that we can use one programming language and one codebase to create two different apps (IOS and Android). We have used Flutter SDKs to  build high-performance, high-fidelity apps for iOS, Android, Web, and Desktop from a single codebase. Flutter is all about 'Widgets' -- a widget can be a Structural element like a button or menu, it can be a Stylistic element like a font or color, or a layout among many other things. Widgets are the basic building blocks of a Flutter app and it is an immutable declaration of part of the UI. Through learning and applying the knowledge, I have made some small interesting projects as well as 1 large project that is Food Delivery App.

