\section*{Abstract}
\addcontentsline{toc}{section}{Abstract}

The transcript result processing and transfer is been a problem for the administrative inmost universities relating to the fact that information are been misplaced, the staff could spend a lot of time trying to locate a student’s record and the delay in transfer of the documents. 
Over the years, record keeping was done manually, keeping paper-based documents of all students’ academic information. This system however has proven inefficient because it could not cater for unforeseen circumstances like fire accident, house demolishing or even the most obvious one - the student’s record going missing. Researchers have come up with more effective ways of solving the paper problem, which led to several web-based student information management systems. However, these researchers did not fully eradicate the paper problem because the process still required an initial printing, then scanning of academic records which served as inputs into the system. Also, there was an increase in the occurrence of service unavailability because all storage and processes came from the same location, making the server vulnerable to unforeseen circumstances like power outage, loss of network connection and system malfunction.\\ 

In view of this problem an automated transcript system was developed using Blockchain, IPFS, python, Flask. The new system developed has quickened the processing and transfer of transcripts and also reduce loss of data. Since it is a pilot implementation, much more features can be added at large scale.


\clearpage